Omics-based Single Step Trait Prediction

### 2017-09-14 paper/manuscript.tex
paper-loocv, update loocv

For the hybrid data, LOOCV was carried out as follows:
Let $D$ and $F$ denote the set of parental inbred lines from the Dent and the 
Flint group, respectively.
Further, let $H \cap [D \times F]$ denote the set of hybrids from crosses 
between $D$ and $F$.
Let $H_{i \times j}$ denote the test set hybrid to be predicted.
We can then define the parents of the training set hybrids as
$D_{i} = D \setminus \{i\}$ and $F_{j} = F \setminus \{j\}$, respectively.
The training set is then defined as 
$H_{TRN}(x \times j) = H \cap (D_{i} \times F_{j})$.

We judged the performance of each model by looking at its predictive ability,
which is calculated as $\rho(\mathbf{y}, \mathbf{\hat{y}})$, where 
$\mathbf{\hat{y}}$ is the vector of predicted values from each LOOCV run.

Standard errors for the predictive abilities were calculated by bootstrapping
predictive and observed values 1,000 times using the \emph{R} package 
\emph{boot}~\cite{Canty2017}.

>>>>

For the hybrid data, LOOCV was carried out as follows:
Let $D$ and $F$ denote the set of parental inbred lines from the Dent and the 
Flint group, respectively.
Further, let $H \cap [D \times F]$ denote the set of hybrids from crosses 
between $D$ and $F$.
Note that $H$ does not comprise all possible crosses between $D$ and $F$,
which would have been $142 \times 103 = 14,626$ hybrids, but a subset of 1,521
hybrids.
Let $H_{i \times j}$ denote the hybrid to be predicted.
We can then define the parents of the training set hybrids as
$D_{i} = D \setminus \{i\}$ and $F_{j} = F \setminus \{j\}$, respectively.
The training set is then defined as 
$H_{TRN}(i \times j) = H \cap (D_{i} \times F_{j})$.

We judged the performance of each model by looking at its predictive ability,
which is calculated as $\rho(\mathbf{y}, \mathbf{\hat{y}})$, where 
$\mathbf{\hat{y}}$ is the vector of predicted values for all genotypes.

Standard errors for the predictive abilities were calculated by bootstrapping
the predicted and observed values 1,000 times using the \emph{R} package 
\emph{boot}~\cite{Canty2017}.
